The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-05-23 article.tex
Update figures
Update text

The PBD model has five biological parameters (see \ref{table:parameters}), 
which we explore in a factorial fashion, excluding some combinations. 
We only simulate a PBD process for phylogenies in which
speciation initiation exceeds extinction rate ($b_i > \mu_i$ and $b_g > \mu_g$),
and in which the expected number of extant good species is less than 1000.
\textbf{[NOTE: accoring to Rampal this has been solved analytically (for the Protracted Birth and Death model). Where?]}.
We use 1000 good species as a threshold, to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are based on the parameter sets used by 
\cite{etienne2014}, as these parameters were shown to result in reasonably
sized phylogenies and using the same set allows us to compare results. 
For the speciation initiation rates of good and incipient species, $b_g$ and $b_i$ 
respectively, we use $0.1$, $0.5$ and $1.0$ speciation initiation events per good/incipient species per time unit.
The speciation completion rates we use are $0.1$, $0.3$, $1.0$ and $10^9$ speciation completion
events per (incipient species) species per time unit. We use $10^9 \approx \infty$
to mimic the BD model, because the PBD model reduces to the BD model for $\lambda = \infty$.
This allows us to measure the baseline error, 
which is the difference between inferred tree and true species tree that arises purely due to noise 
because the generating model and the model used in inference are identical in this case.
The extinction rates of good and incipient species, $\mu_g$ and $\mu_i$ respectively, 
that we use are $0.0$, $0.1$, $0.2$ and $0.4$ 
extinction events per good/incipient species per time unit.

@@

\begin{figure}[!htbp]
  \includegraphics[width=0.8\textwidth]{fig_nltt_stats_per_setup.png}
  \caption{
    nLTT statistic distribution per biological parameter set, using the
    balanced data set
  }
\end{figure}

>>>>

\textbf{[NOTE: I will propose different parameter combinations, due to computational and aesthetic problems]}
The PBD model has five biological parameters (see \ref{table:parameters}), 
which we explore in a factorial fashion, excluding some combinations. 
We only simulate a PBD process for phylogenies in which
speciation initiation exceeds extinction rate ($b_i > \mu_i$ and $b_g > \mu_g$),
and in which the expected number of extant good species is less than 1000.
\textbf{[NOTE: accoring to Rampal this has been solved analytically (for the Protracted Birth and Death model). Where?]}.
We use 1000 good species as a threshold, to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are based on the parameter sets used by 
\cite{etienne2014}, as these parameters were shown to result in reasonably
sized phylogenies and using the same set allows us to compare results. 
For the speciation initiation rates of good and incipient species, $b_g$ and $b_i$ 
respectively, we use $0.1$, $0.5$ and $1.0$ speciation initiation events per good/incipient species per time unit.
The speciation completion rates we use are $0.1$, $0.3$, $1.0$ and $10^9$ speciation completion
events per (incipient species) species per time unit. We use $10^9 \approx \infty$
to mimic the BD model, because the PBD model reduces to the BD model for $\lambda = \infty$.
This allows us to measure the baseline error, 
which is the difference between inferred tree and true species tree that arises purely due to noise 
because the generating model and the model used in inference are identical in this case.
The extinction rates of good and incipient species, $\mu_g$ and $\mu_i$ respectively, 
that we use are $0.0$, $0.1$, $0.2$ and $0.4$ 
extinction events per good/incipient species per time unit.

@@

\begin{figure}[!htbp]
  \includegraphics[width=0.8\textwidth]{fig_general.png}
  \caption{
    nLTT statistic distribution per biological parameter set, using the
    balanced data set
  }
\end{figure}
